PS753 Glossary

### 2022-01-30 _academics/ps753-glossary/ps753-glossary.Rmd
lowercase ps743 you idiot
Add pseudo top-level nav for /academics
typo

<p style="background: #eee">
[PS 753](../PS753/index.html)
&gt; Glossary
</p>

@@

and $j$ similarly as a set of $n$ elements, except that $j$ cannot equal $i (a node cannot connect to itself):
$$j \in 1, 2, 3 \dots n, i \ne j$$

>>>>

<p style="background: #eee">
Academics &gt; [PS 753](../ps753/index.html)
&gt; Glossary
</p>

@@

and $j$ similarly as a set of $n$ elements, except that $j$ cannot equal $i$ (a node cannot connect to itself):
$$j \in 1, 2, 3 \dots n, i \ne j$$
